\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-28 paper.tex
Update on Overleaf.

\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor} as part of a system for a large scale study with 150 children. \uwds {\tt spatial\_relations} module is used to visualise counting tasks and teach spatial words for a second language. \uwds's loose coupling allows for easy integration with the {\tt spatial_relations} between either an object recognition system that would allow for use in a physical environment(

>>>>

\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor} as part of a system for a large scale study with 150 children. \uwds {\tt spatial\_relations} module is used to visualise counting tasks and teach spatial words for a second language. \uwds's loose coupling allows for easy integration with the {\tt spatial_relations} between either an object recognition system that would allow for use in a physical environment(Figure~\ref{fig|l2torexample})
